Supporting Information: Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling.

### 2020-01-27 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Changed duplicate reference

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N100.pdf}
  \caption{100 Independent Trajectories}\label{fig:N100}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N1000.pdf}
  \caption{1000 Independent Trajectories}\label{fig:N1000}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N5000.pdf}
  \caption{5000 Independent Trajectories}\label{fig:N5000}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_N9984.pdf}
  \caption{10000 Independent Trajectories}\label{fig:N10000}
  \end{subfigure}
  \caption{Even using a small number of independent trajectories, one can
  reliably calculate flux as a function of pore length. The uncertainty in
  the flux curves decreases as we add more independent trajectories.}\label{fig:flux_curve_sensitivity}
  \end{figure}
  %MRS8: is there a way to make it easier to see the fact that the data is relatively independent of length?
  %MRS8: Right now, you essentially have to scan between the 4 charts to see the numbers are about right. Maybe
  %MRS8: organize it so that the 4 charts are for 4 molecules, and each chart shows plot of 
  %MRS8: trajectory number vs pore length, so one can see that the value stays about the same except for uncertainty as 
  %MRS8: number of trajectories changes
  % equations here 
  % Analytical CDF: https://journals.aps.org/pre/pdf/10.1103/PhysRevE.73.046104
  % Analytical MFPT https://journals.aps.org/pre/pdf/10.1103/PhysRevE.62.6065
  % Figures: mfpt_pdf.pdf and mfpt_cdf.pdf

>>>>

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_URE.pdf}
  \caption{urea}\label{fig:Nsensitivity_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_ACH.pdf}
  \caption{acetic acid}\label{fig:Nsensitivity_ACH}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_GCL.pdf}
  \caption{ethylene glycol}\label{fig:Nsensitivity_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Nsensitivity_MET.pdf}
  \caption{mehtanol}\label{fig:Nsensitivity_MET}
  \end{subfigure}
  \caption{Even using a small number of independent trajectories, one can
  reliably estimate solute flux across a pore 10 nm long. The uncertainty in 
  the flux values decreases as we add more independent trajectories.
  }\label{fig:flux_curve_sensitivity}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_URE.pdf}
  \caption{urea}\label{fig:Asensitivity_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_ACH.pdf}
  \caption{acetic acid}\label{fig:Asensitivity_ACH}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_GCL.pdf}
  \caption{ethylene glycol}\label{fig:Asensitivity_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_Asensitivity_MET.pdf}
  \caption{mehtanol}\label{fig:Asensitivity_MET}
  \end{subfigure}
  \caption{Even using a small number of independent trajectories, one can
  reliably estimate solute flux across a pore 10 nm long. The uncertainty in 
  the flux values decreases as we add more independent trajectories.
  }\label{fig:A_sensitivity}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_URE.pdf}
  \caption{urea}\label{fig:betasensitivity_URE}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_ACH.pdf}
  \caption{acetic acid}\label{fig:betasensitivity_ACH}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_GCL.pdf}
  \caption{ethylene glycol}\label{fig:betasensitivity_GCL}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flux_curves_betasensitivity_MET.pdf}
  \caption{mehtanol}\label{fig:betasensitivity_MET}
  \end{subfigure}
  \caption{Even using a small number of independent trajectories, one can
  reliably estimate solute flux across a pore 10 nm long. The uncertainty in 
  the flux values decreases as we add more independent trajectories.
  }\label{fig:beta_sensitivity}
  \end{figure}

%  \begin{figure}
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{flux_curves_N100.pdf}
%  \caption{100 Independent Trajectories}\label{fig:N100}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{flux_curves_N1000.pdf}
%  \caption{1000 Independent Trajectories}\label{fig:N1000}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{flux_curves_N5000.pdf}
%  \caption{5000 Independent Trajectories}\label{fig:N5000}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{flux_curves_N9984.pdf}
%  \caption{10000 Independent Trajectories}\label{fig:N10000}
%  \end{subfigure}
%  \caption{Even using a small number of independent trajectories, one can
%  reliably calculate flux as a function of pore length. The uncertainty in
%  the flux curves decreases as we add more independent trajectories.}\label{fig:flux_curve_sensitivity}
%  \end{figure}
  %MRS8: is there a way to make it easier to see the fact that the data is relatively independent of length?
  %MRS8: Right now, you essentially have to scan between the 4 charts to see the numbers are about right. Maybe
  %MRS8: organize it so that the 4 charts are for 4 molecules, and each chart shows plot of 
  %MRS8: trajectory number vs pore length, so one can see that the value stays about the same except for uncertainty as 
  %MRS8: number of trajectories changes
  % equations here 
  % Analytical CDF: https://journals.aps.org/pre/pdf/10.1103/PhysRevE.73.046104
  % Analytical MFPT https://journals.aps.org/pre/pdf/10.1103/PhysRevE.62.6065
  % Figures: mfpt_pdf.pdf and mfpt_cdf.pdf
